How to measure the radial velocity of a star:\\The invariant-spectrum case

### 2022-02-06 paper/main.tex

% to-do list
% ----------
% - Look for all instances of HOGG, BEDELL, and CITE.
% - Make an acronym command and fix CLRB and all other acronyms.
% - Be sure to discuss SNR in a continuum resolution element, as well as in a pixel.
%.- Make sure that, for any assumption that is explicitly tested, the forthcoming test is mentioned when the assumption is introduced.
% - Are we clear that we exponentiate the model to get the true data expectation?
% - Are we consistent in our use of Doppler shift, radial velocity, and redshift and so on?
% - Are we sensible in our use of first person?
% - Do we address the relationship between our tiny spectral segment and a full spectrograph? Get scalings. Etc.
% - Make sure all figures are explicitly referred to in the text.
% - I believe we are inconsistent with the tense. Always present or always past? Decide and audit / fix. Probably present is better.

@@

@@

\begin{figure}[tp]
  \begin{mdframed}
    \begin{center}
    \includegraphics[width=\textwidth]{../notebook/telluricmodel.png}
    \includegraphics[width=\textwidth]{../notebook/telluric.png}
    \end{center}
    \caption{The top panels show the introduced telluric effect in blue, in comparison with the true spectral template (in red, repeated from \figref{fig:datazoom}). The bottom panel is the same \figref{fig:ccfrvs} but now showing cross-correlation results after this unmodeled telluric contamination is introduced.\label{fig:variable}}
  \end{mdframed}
\end{figure}

@@

>>>>

% to-do list
% ----------
% - Look for all instances of HOGG, BEDELL, and CITE.
% - Make an acronym command and fix CLRB and all other acronyms.
% - Be sure to discuss SNR in a continuum resolution element, as well as in a pixel.
%.- Make sure that, for any assumption that is explicitly tested, the forthcoming test is mentioned when the assumption is introduced.
% - Are we clear that we exponentiate the model to get the true data expectation?
% - Are we consistent in our use of Doppler shift, radial velocity, and redshift and so on?
% - Are we sensible in our use of first person?
% - Do we address the relationship between our tiny spectral segment and a full spectrograph? Get scalings. Etc.
% - Make sure all figures are explicitly referred to in the text.
% - I believe we are inconsistent with the tense. Always present or always past? Decide and audit / fix. Probably present is better.
% - I think we should only measure Doppler shift, and never RV. Right??
% - Cite Vakili et al for the parabola trick, maybe?
% - Make the comment that the detailed noise model doesn't matter -- the CCF RVs are as good as the ML RVs.

@@

HOGG: Refer to \figref{fig:calibration}

@@

HOGG: Refer to \figref{fig:telluric}.

\begin{figure}[tp]
  \begin{mdframed}
    \begin{center}
    \includegraphics[width=\textwidth]{../notebook/telluricmodel.png}
    \includegraphics[width=\textwidth]{../notebook/telluric.png}
    \end{center}
    \caption{The top panels show the introduced telluric effect in a thick blue line, in comparison with the true spectral template (thin red line, repeated from \figref{fig:datazoom}). The telluric template (thick blue) stays fixed in logarithmic wavelength $x$ while the spectral template (thin red) Doppler shifts. The bottom panel is the same \figref{fig:ccfrvs} but now showing cross-correlation results after this unmodeled telluric contamination is introduced.\label{fig:telluric}}
  \end{mdframed}
\end{figure}

@@

HOGG: Refer to \figref{fig:variable}.
